---
title: "Figures' note for N-back ipRGC study"
author: "Yuta Suzuki, Shigeki Nakauchi, Hsin-I Liao"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  word_document:
    # toc: true
    # reference_docx: doc_templete.docx
  # slidy_presentation:
  # pdf_document:
    # css: style.css
params:
  year: 2025
editor_options: 
  markdown: 
    wrap: 72
---

# Article information

Yuta Suzuki$^1$, Shigeki Nakauchi$^2$, Hsin-I Liao$^1$

$^1$ NTT Communication Science Laboratories, NTT Corporation, Atsugi
243-0198, Japan

$^2$ Department of Computer Science and Engineering, Toyohashi
University of Technology, 1-1 Hibarigaoka Tempaku, Toyohashi, Aichi
441-8580, Japan

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, echo=FALSE,warning=FALSE,include=FALSE}

SIZE_FONT = 14
numOfTertile = 3

nsFlag = T
saveFig = T

#### file loading
CairoFonts(regular = "Times New Roman", bold="Times New Roman Bold")

rootFolder = paste0("../[Python]PreProcessing/data")

folderName = list.files(rootFolder, full.names=T)
folderName = folderName[length(folderName)]

date = unlist(strsplit(folderName,"/"))
date = date[length(date)]

dataFolder = paste0("./data/",date,"/")
saveFolder = paste0("./figure/",format(Sys.time(), '%Y%m%d'),"/")

cfg = fromJSON(file=paste0(folderName,"/cfg.json"))

TIME_START = cfg$TIME_START
TIME_END = cfg$TIME_END
WIN_ANALYSIS = cfg$TIME_END

sTime = cfg$WID_BASELINE[[1]][1]
eTime = cfg$TIME_END

if(!dir.exists(saveFolder)){
  dir.create(saveFolder)
}

# average -----------------------------------------------------------------

runName = c("Run1","Run2","Run3","Run4","Run5","Run6")

anovaTabAll = list()
p_all = list()


annotation_df <- data.frame(
  Nback = c("1-back","2-back"),
  light = c("low ipRGC","low ipRGC"),
  start = c("low ipRGC","low ipRGC"),
  end = c("high ipRGC","high ipRGC"),
  y = c(99),
  # label = c("n.s.",paste0("p=",round(ttest_2back$ttest$p.value,3)))
  label = c("n.s.","*")
)

config <- list(lim_x = c(0,1),
               lim_y = c(2,4),
               alpha = 0.1,
               stride = 0.1,
               label_x = "Time [sec]",
               label_y = "Pupil size[a.u.]",
               title = "",
               linetype = T,
               shape=F,
               # grCol = c("#738CD9","#222222")
               grCol = c("#AB004A","#222222")
)

```

\newpage

# Results

## Stimulus tuning experiment

### load data

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_behavior_ave <- load_json_dataframe(folderName, "df_behavior_ave.json")
df_max <- load_json_dataframe(folderName, "df_max.json")
df_sameLight <- load_json_dataframe(folderName, "stimSelect_same.json")
df_stim_tune <- load_json_dataframe(folderName, "spectra.json")
df_light_spectra <- load_json_dataframe(folderName, "spectra_all.json")
df_projector_spectra <- load_json_dataframe(folderName, "spectra_projector")
df_brightness <- load_json_dataframe(folderName, "spectra_flux.json")

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

################################ stimulus tuning ################################ 
df_behavior_ave$sub = factor( df_behavior_ave$sub ,levels = unique(df_behavior_ave$sub))
df_max$sub = factor( df_max$sub ,levels = unique(df_max$sub))

p_all$stimulus_tuning <- ggplot(df_behavior_ave,aes(x = Color, y = ans, color=sub,group=sub))+
  geom_point(size = 3)+
  geom_line(size=0.5)+
  geom_point(data=df_max,aes(x=Color, y=ans, color=sub, group=sub),size = 6)+
  xlab("Color candidate (low ipRGC light)") + ylab("Probability of 'identical'")

config$ylim = round(seq(0,1,0.2),4)
config$ylim_stride = 0.02

config$xlim = round(seq(1,12,1),4)
config$xlim_stride = 0.1

# display.brewer.all()

p_all$stimulus_tuning = setEmptyStyle(p_all$stimulus_tuning,config)+
  scale_x_continuous(breaks = config$xlim)

p_all$stimulus_tuning$size = c(10,8)

################################ Brightness ################################ 

df_sameLight$light = "low ipRGC"
df_sameLight = rbind(df_sameLight[1,],df_sameLight)
df_sameLight[1,]$light="high ipRGC"
df_sameLight[1,]$Y = 713.557

df_Y = aggregate( Y ~ light, data = df_sameLight, FUN = 'mean')
df_sd = aggregate( Y ~ light, data = df_sameLight, FUN = 'sd')

################################ same light ################################ 

# df$selected = df$selected + 1
# df$selected = factor( df$selected ,levels=sort(unique(df$selected)))
# 
# df$light = factor( df$light ,levels=c("low ipRGC","high ipRGC"))

p_all$sameLight <- ggplot(df_sameLight,aes(x = Color, y = ans))+
  geom_boxplot()+
  ylab("Probability of 'identical'")

config$ylim = round(seq(0,1,0.2),4)
config$ylim_stride = 0.02

config$xlim = round(seq(0,1,1),4)
config$xlim_stride = 0.1

p_all$sameLight = setEmptyStyle(p_all$sameLight,config)+
  scale_x_continuous(breaks = config$xlim)

p_all$sameLight$size = c(8,8)
# p <- ggplot(df,aes(x = x, y = y,color = size, group = Light)
#  eval(parse(text=paste0("p = p + geom_point(size = 3)")))

################################ xy coordinates ################################ 


df_light_show = df_stim_tune

df_light_show$index = NULL
df_light_show$wavelength.nm. = NULL
df_light_show$power = NULL
df_light_show$X = NULL
df_light_show$Z = NULL
df_light_show$L. = NULL
df_light_show$a. = NULL
df_light_show$b. = NULL
df_light_show$size = NULL

b = df_stim_tune[df_stim_tune$Light != "high ipRGC",]$ipRGC
a = df_stim_tune[df_stim_tune$Light == "high ipRGC",]$ipRGC

contrast_ipRGC =  (a-b)/(a+b)*100

x1 = df_stim_tune[(df_stim_tune$Light=="high ipRGC"),]$Y
x2 = df_max$Y

x1 = rep(x1,length(x2))

ttest_luminance = getTtestSummary(x1,x2)
# , size = size
df_stim_tune[df_stim_tune["Light"]=="high ipRGC",]$size = max(df_stim_tune$size)

# p_all$xy <- ggplot(df_stim_tune,aes(x = x, y = y, color = size))+
p_all$xy <- ggplot(df_stim_tune,aes(x = x, y = y, size = size,color=Light))+
  scale_size(range = c(5, 15))+
  # geom_point(size=10)+
  geom_point()+
  # coord_fixed(ratio = 1)+ 
  scale_color_manual(values = c(config$grCol[1],rep(config$grCol[2],12)))
# scale_color_gradient(low=brewer.pal(6, "YlOrRd")[2],high=brewer.pal(6, "YlOrRd")[6])
# scale_color_gradient(low=brewer.pal(8, "Greys")[2],high=brewer.pal(8, "Greys")[8])

p_all$xy = p_all$xy +
  geom_point(x=df_stim_tune[df_stim_tune$Light=="high ipRGC",]$x,
             y=df_stim_tune[df_stim_tune$Light=="high ipRGC",]$y,
             size=10,color="black")

config$ylim = round(seq(0.228,0.252,0.004),4)
config$ylim_stride = 0.01

config$xlim = round(seq(0.4,0.428,0.004),4)
config$xlim_stride = 0.01

# display.brewer.all()

p_all$xy = setEmptyStyle(p_all$xy,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1)
  )+
  coord_equal()

# theme(
# legend.justification=c(0,1), legend.position=c(0,1),
# legend.justification=c(0,1), legend.position=c(1,1),
# legend.position="right",
# legend.title=element_blank(),
# legend.position="none",
# axis.text.x = element_text(angle = 30, hjust = 1)
# )

p_all$xy$size = c(12,12)


################################ ipRGC ################################

# c("#FED976","#F7C069","#EFA75D","#DD7446","#BD0026")

# p = c("#AB004A","#BD0026","#FED976","#F7C069","#EFA75D","#FED976","#F7C069",
#       "#FED976","#FED976","#F7C069","#EFA75D","#DD7446","#FED976")

p = c("#AB004A","#F0F0F0","#000000","#525252","#737373","#000000","#525252",
      "#000000","#000000","#525252","#737373","#BDBDBD","#000000")

# brewer.pal(10, "Greys")

df_light_spectra$linetype = "high ipRGC"
df_light_spectra[df_light_spectra$Light!="high ipRGC",]$linetype = "low ipRGC"

df_light_spectra$linetype = factor( df_light_spectra$linetype ,levels=c("low ipRGC","high ipRGC"))

config$linetype=T
p_all$ipRGC = dispLineGraph(df_light_spectra,config,"ipRGC",c("linetype"),12)+
  xlab("") + ylab("ipRGC contrast")

# p_all$ipRGC <- ggplot(df_light_spectra,aes(x = linetype, y = ipRGC, color=Light))+
#   geom_point(size=5)+
#   xlab("") + ylab("ipRGC contrast")+
#   scale_color_manual(values = p)

config$ylim = round(seq(0.6,1.2,0.1),4)
config$ylim_stride = 0.01

config$xlim = round(seq(1,2,1),4)
config$xlim_stride = 0.1

p_all$ipRGC = setEmptyStyle(p_all$ipRGC,config)
# scale_x_continuous(breaks = config$xlim)

p_all$ipRGC$size = c(6,5)

################################ spectra lights ################################

df_light_spectra$linetype = "0.target"
df_light_spectra[df_light_spectra$Light!="high ipRGC",]$linetype = "1.reference"
config$label_y = expression(paste("Radiance [W*sr"^{"-1"},"*m"^{"-2"} ,"]" ))
config$label_x = expression("Wavelength[nm]")

p_all$spectra <- ggplot(df_light_spectra,aes(x = wavelength.nm., y = power, color = Light,linetype=linetype))+
  xlab(config$label_x) + ylab(config$label_y) +
  #   # scale_size(range = c(5, 25))+
  geom_line()

config$ylim = round(seq(0,0.04,0.01),4)
config$ylim_stride = 0.001

config$xlim = round(seq(380,780,40),4)
config$xlim_stride = 2

# display.brewer.all()

p_all$spectra = setEmptyStyle(p_all$spectra,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    # legend.justification=c(1,1), legend.position=c(1,0),
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

p_all$spectra$size = c(9,3)

################################ spectra projector ################################


p = c("#325C9B","#83AE27","#D95635","#81C5D8","#83AE27","#D95635")

df_projector_spectra$primary = "ipRGC"
df_projector_spectra[grepl("blue", df_projector_spectra$Light),]$primary = "S-cone"

# df_projector_spectra$linetype = "0.target"
# df_projector_spectra[df_projector_spectra$Light!="high ipRGC",]$linetype = "1.reference"
# config$label_y = expression(paste("Radiance [W*sr"^{"-1"},"*m"^{"-2"} ,"]" ))
# config$label_x = expression("Wavelength[nm]")

p_all$spectra_projector <- ggplot(df_projector_spectra,aes(x = wavelength.nm., y = power, color = Light))+
  xlab(config$label_x) + ylab(config$label_y) +
  scale_color_manual(values = p)+
  geom_line()+
  facet_grid(primary ~ . )

config$ylim = round(seq(0,0.1,0.02),4)
config$ylim_stride = 0.001

config$xlim = round(seq(380,780,40),4)
config$xlim_stride = 2

# display.brewer.all()

p_all$spectra_projector = setEmptyStyle(p_all$spectra_projector,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

p_all$spectra_projector$size = c(10,6)

```

### desription

In order to tune a metameric stimulus which has a higher ipRGC contrast
but independent from the cones activities taking into account individual
differences in cone distribution (reference), we first identified a
metermaric light with high ipRGC light by 2AFC experiment. Figure 2D
shows the CIE xy of the candidate low ipRGC light and number of
participants in each light that was judged to be regarded as a metameric
to the high ipRGC light. In all subjects, the selected light was
reported as being perceived as the same color at least once
(Supplementary Figure 1). The averaged luminance of selected low ipRGC
calculated based upon CIE photoreceptor sensitivities was
`r round(mean(df_max$Y),3)` $\pm$ `r round(sd(df_max$Y),3)` cd/m2. The
averaged Michelson contrast of ipRGC across used metamar pair was
`r round(mean(contrast_ipRGC),3)` $\pm$
`r round(sd(contrast_ipRGC),3)`%.

CIE xy
(`r round(df_light_show[df_light_show$Light=="high ipRGC",]$x,3)`,
`r round(df_light_show[df_light_show$Light=="high ipRGC",]$y,3)`)

<!-- To identify a metermaric light with high ipRGC light, participants were asked if the two presented light are identical or different by 2AFC.  -->

<!-- Figure S1 shows the averaged judgement in each light. the black circle shows the selected light.  -->

<!-- When the probability of two or more light are the same, the most close measured CIE xy light are employed.  -->

<!-- Figure 2D shows CIE xy coordinate of the chosen low ipRGC light that was judged to be metameric to the high ipRGC light. There is no luminance differences between high and low ipRGC light (`r showTtestSummary(ttest_luminance)`).  -->

<!-- `r round(mean(df_sameLight$ans),3)` $\pm$ `r round(sd(df_sameLight$ans),3)` -->

<!-- `r kable(df_light_show)` -->

## Brightness

### code

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_brightness_ave = aggregate( Y ~ sub, data = df_brightness, FUN = 'mean')
df_brightness_ave$ipRGC_Y = df_Y[df_Y$light=="high ipRGC",]$Y

df_brightness_ave$ratio = df_Y[df_Y$light=="high ipRGC",]$Y

p_all$brightness <- ggplot(df_brightness_ave,aes(x = 0, y = Y/ipRGC_Y*100)) +
  xlab("") + 
  ylab("Brightness ratio [%]") +
  #   # scale_size(range = c(5, 25))+
  geom_boxplot()+
  geom_beeswarm()
# geom_jitter(
#   width = 0.05,
#   height = 0,
#   size = 3
# )

config$ylim = round(seq(80,160,20),4)
config$ylim_stride = 2

config$xlim = round(seq(0,0,1),4)
config$xlim_stride = 0.1

p_all$brightness = setEmptyStyle(p_all$brightness,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

p_all$brightness$size = c(6,5)

x1 = df_brightness_ave$Y
x2 = df_Y[df_Y$light == "high ipRGC",]$Y
x2 = rep(x2,length(x1))

ttest_brightness = getTtestSummary(x1,x2)


```

### desription

By using the metermaric light in each participants, we confirmed the
activation of ipRGC by the brightness judgement experiment. Figure 1E
shows the ratio of adjusted luminance to high ipRGC light. The high
ipRGC light was perceived around 20% more brighter than the low ipRGC
light (`r showTtestSummary(ttest_brightness)`), consistent with previous
studies (Brown et al., 2012, Yamakawa et al.,2019).

## Pupil size

### load data

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# df_pupil_all <- load_json_dataframe(folderName, "data_timeCourse.json")
df_pupil <- load_json_dataframe(folderName, "data_timeCourse_ave.json")

```

### code

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# f = list.files(folderName, pattern = "data_timeCourse.json", full.names=T)
# df_pupil = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_pupil)){
#   df_pupil[[iName]] = unlist(df_pupil[[iName]])
# }
# df_pupil = as.data.frame(df_pupil)
# 
# df_pupil = aggregate( Pupil.mm. ~ sub*Time.s.*light*Nback, data = df_pupil, FUN = 'mean')


# config <- list(lim_x = c(min(df_pupil$Time.s.),max(df_pupil$Time.s.)),
#                lim_y = c(2,4),
#                alpha = 0.1,
#                stride = 0.1,
#                label_x = "Time [sec]",
#                label_y = "Pupil size[a.u.]",
#                title = "",
#                linetype = T,
#                grCol = c("#738CD9","#222222")
# )

# df_pupil$Run = runName[df_pupil$Run]

# df_pupil$data_x = df_pupil$Time.s.
# p_all$pupilTimeCourse <- disp(df_pupil,config,"Pupil.mm.",1,c("light","Nback")) +
#   # facet_grid(sub ~ .)+
#   theme(
#     # legend.justification=c(0,1), legend.position=c(0,1),
#     legend.justification=c(0,1), legend.position=c(1,1)
#   )
# 
# config$ylim = round(seq(2.5,3.5,0.1),4)
# config$ylim_stride = 0.01
# config$xlim = round(seq(min(df_pupil$Time.s.),max(df_pupil$Time.s.),25),2)
# config$xlim_stride = 2.5
# 
# config$label_x = ""
# p_all$pupilTimeCourse = setEmptyStyle(p_all$pupilTimeCourse,config)+
#   scale_x_continuous(breaks = config$xlim)
# 
# p_all$pupilTimeCourse$size = c(6,10)


# # average -----------------------------------------------------------------

config$grCol = c("#222222","#AB004A",rep("#101010",52))


df = aggregate( Pupil.mm. ~ sub*light*Nback, data = df_pupil, FUN = 'mean')

anovakun(df,"sAB",long=T, peta=T)


df$light = factor(df$light ,levels = unique(df$light))
df$sub = factor(df$sub,levels = unique(df$sub))
df$Nback = factor(df$Nback,levels = unique(df$Nback))

bf_table = anovaBF(Pupil.mm. ~ light*Nback + sub, data=df, whichRandom = "sub",progress=FALSE)

x1 = df[(df$Nback=="1-back")&(df$light=="high ipRGC"),]$Pupil.mm.
x2 = df[(df$Nback=="1-back")&(df$light=="low ipRGC"),]$Pupil.mm.

ttest_1back = getTtestSummary(x1,x2)

x1 = df[(df$Nback=="2-back")&(df$light=="high ipRGC"),]$Pupil.mm.
x2 = df[(df$Nback=="2-back")&(df$light=="low ipRGC"),]$Pupil.mm.

ttest_2back = getTtestSummary(x1,x2)

annotation_df$label = c(ttest_1back$sig,ttest_2back$sig)
annotation_df$y = 3.1

df$light = factor( df$light ,levels=c("low ipRGC","high ipRGC"))

config$linetype=T
config$label_x=""
config$label_y="Pupil size [mm]"

p_all$pupil_ave = dispLineGraph(df,config,"Pupil.mm.",c("light","light","Nback"))+
  facet_grid(. ~ Nback)+
  geom_signif(data=annotation_df,
              aes( xmin=start,xmax=end,annotations=label,y_position=y),
              textsize = 5, size=0.2, tip_length = 0.00,color="black",family=fontFamily,manual = TRUE)
# +
#   geom_line(data=df,
#             size = 0.1,
#             alpha = 0.2,
#             aes(x = light, y = Pupil.mm., group = interaction(sub,Nback), color = interaction(sub,Nback)))+
#   geom_point(data=df,
#             size = 0.1,
#             alpha = 0.1,
#             aes(x = light, y = Pupil.mm., 
#                 group = interaction(sub,light,Nback), color = interaction(sub,Nback)))

config$ylim = round(seq(2.6,3.2,0.1),4)
config$ylim_stride = 0.01
config$xlim = round(seq(1,2,1),4)
config$xlim_stride = 0.5

p_all$pupil_ave = setEmptyStyle(p_all$pupil_ave,config)+
  theme(
    # legend.justification=c(0,1), legend.position=c(0,1),
    # legend.justification=c(0,1), legend.position=c(1,1),
    # legend.position="right",
    # legend.title=element_blank(),
    legend.position="none",
    axis.text.x = element_text(angle = 30, hjust = 1)
  )

p_all$pupil_ave$size = c(6,6)

```

### desription

Pupil size was measured using an infrared camera while participants were
lighted low and high ipRGC light and engaged in 1- or 2-back task (see
Method). Figure 2B illustrates the averaged pupil size during 1- and
2-back task in each lighting condition. A two-way repeated measures
ANOVA for the main effect of light showed that the pupil size for high
ipRGC light was significantly smaller than for low ipRGC light
(`r showAnovaSummary(forDrawingSigANOVA,bf_table,2,1)`), consistent with
the previous studies as an effect of activation of ipRGC. Following post
analysis also showed that the pupil size in both N-back task for high
ipRGC light was smaller than for low ipRGC light
(1-back: `r showTtestSummary(ttest_1back)`; 2-back: `r showTtestSummary(ttest_2back)`).
In addition, the pupil size of 2-back task was larger than of 1-back
task as reported an effect of cognitive load differences previously
(`r showAnovaSummary(forDrawingSigANOVA,bf_table,4,2)`), as reported
here and elsewhere.

## Accuracy

### load data

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_response  <- load_json_dataframe(folderName, "df_target_mean.json")
df_nonTarget <- load_json_dataframe(folderName, "df_nonTarget.json")
df_pupil     <- load_json_dataframe(folderName, "data_timeCourse_ave.json")
df_targetAll <- load_json_dataframe(folderName, "df_targetAll")
df_RT        <- load_json_dataframe(folderName, "df_RT.json")

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

################################ load data ################################

data_anova = aggregate( hit ~ sub*light*Nback, data = df_response, FUN = 'mean')
anovakun(data_anova,"sAB",long=T, peta=T)

hit_anova = forDrawingSigANOVA

modelList = c(
  "hit ~ light + (1| sub)"
)

################################ LME ################################ 

estimateAll = NULL
for(inback in unique(df_response$Nback)){
  tmp_df = df_response[(df_response$Nback==inback),]
  
  aic_res = NULL
  for( m in modelList){
    # eval(parse(text=paste0(" model_cand <- lmer(",m,", data=tmp_df)")))
    eval(parse(text=paste0(" model_cand <- lmer(",m,", data=tmp_df)")))
    sm = summary(model_cand)
    print(sm)
  }
}

################################ hit rate ################################ 

df_response$light = factor(df_response$light ,levels = unique(df_response$light))
df_response$sub = factor(df_response$sub,levels = unique(df_response$sub))
df_response$Nback = factor(df_response$Nback,levels = unique(df_response$Nback))

bf_table = anovaBF(hit ~ light*Nback + sub, data=df_response, whichRandom = "sub",progress=FALSE)

x1 = df_response[(df_response$Nback=="1-back")&(df_response$light=="high ipRGC"),]$hit
x2 = df_response[(df_response$Nback=="1-back")&(df_response$light=="low ipRGC"),]$hit

ttest_1back = getTtestSummary(x1,x2)

x1 = df_response[(df_response$Nback=="2-back")&(df_response$light=="high ipRGC"),]$hit
x2 = df_response[(df_response$Nback=="2-back")&(df_response$light=="low ipRGC"),]$hit

ttest_2back = getTtestSummary(x1,x2)

annotation_df$label = c(ttest_1back$sig,ttest_2back$sig)
annotation_df$y = 98

config <- list(lim_x = c(-0.5,TIME_END),
               lim_y = c(5000,8000),
               alpha = 0.1,
               stride = 0.1,
               label_x = "",
               label_y = "Accuracy (% of hit)",
               title = "",
               linetype = T,
               grCol = c("#222222","#AB004A",rep("#101010",54)),
               shape=F
)

df_response$light = factor( df_response$light ,levels=c("low ipRGC","high ipRGC"))
df_response$hit = df_response$hit * 100

p_all$hit = dispLineGraph(df_response,config,"hit",c("light","light","Nback"))+
  facet_grid(. ~ Nback ) +
  geom_signif(data=annotation_df,
              aes( xmin=start,xmax=end,annotations=label,y_position=y),
              textsize = 5, size=0.2, tip_length = 0.00,family=fontFamily,manual = TRUE)

# +
# geom_line(data=df,
#           size = 0.1,
#           alpha = 0.2,
#           aes(x = light, y = hit, group = interaction(sub,Nback), color = interaction(sub,Nback))) +
# geom_point(data=df,
#           size = 0.1,
#           alpha = 0.1,
#           aes(x = light, y = hit, group = interaction(sub,light,Nback), color = interaction(sub,Nback))) 


# config$ylim = round(seq(0.85,1,0.025),4)
# config$ylim_stride = 0.002
# config$ylim = round(seq(85,100,2.5),4)
config$ylim = round(seq(80,100,2.5),4)
config$ylim_stride = 0.25
config$xlim = round(seq(1,2,1),4)
config$xlim_stride = 0.5

p_all$hit = setEmptyStyle(p_all$hit,config)+
  theme(
    # legend.justification=c(0,1), legend.position=c(1,1),
    # legend.position="right",
    legend.position="none",
    # legend.justification=c(0,1), legend.position=c(0,1),
    axis.text.x = element_text(angle = 30, hjust = 1),
    # legend.title=element_blank()
  )

p_all$hit$size = c(6,6)

################################ Cr and FA ################################ 

df_nonTarget$light = factor( df_nonTarget$light ,levels=c("low ipRGC","high ipRGC"))

for( SDT in c("CR","FA")){
  
  eval(parse(text=paste0("data_anova = aggregate( ", SDT," ~ sub*light*Nback, data = df_nonTarget, FUN = 'mean')")))
  
  # anovakun(data_anova,"sAB",long=T, peta=T)
  
  # eval(parse(text=paste0("df_nonTarget$", SDT,"=df_nonTarget$",SDT,"*100")))
  eval(parse(text=paste0("config$label_y = '", SDT," rate(%)'")))
  
  eval(parse(text=paste0("p_all$", SDT,"= dispLineGraph(df_nonTarget,config,'", SDT, "',c('light','light','Nback'))")))
  eval(parse(text=paste0("p_all$", SDT,"= p_all$", SDT,"+facet_grid(. ~ Nback )")))
}

x1 = df_nonTarget[(df_nonTarget$Nback=="2-back")&(df_nonTarget$light=="high ipRGC"),]$FA
x2 = df_nonTarget[(df_nonTarget$Nback=="2-back")&(df_nonTarget$light=="low ipRGC"),]$FA

ttestFA_2back = getTtestSummary(x1,x2)

for(nback in c("1-back","2-back")){ 
  tmp_low_target = df_response[(df_response$Nback==nback)&(df_response$light=="low ipRGC"),]
  tmp_high_target = df_response[(df_response$Nback==nback)&(df_response$light=="high ipRGC"),]
  
  tmp_low = df_nonTarget[(df_nonTarget$Nback==nback)&(df_response$light=="low ipRGC"),]
  tmp_high = df_nonTarget[(df_nonTarget$Nback==nback)&(df_response$light=="high ipRGC"),]
  
  tmp_sig = NULL
  for( SDT in c("hit","miss","CR","FA")){
    
    if ((SDT == "hit") | (SDT == "miss")){
      eval(parse(text=paste0("x1 = df_response[(df_response$Nback=='",nback,"')&(df_response$light=='high ipRGC'),]$", SDT)))
      eval(parse(text=paste0("x2 = df_response[(df_response$Nback=='",nback,"')&(df_response$light=='low ipRGC'),]$", SDT)))
    }else{
      eval(parse(text=paste0("x1 = df_nonTarget[(df_nonTarget$Nback=='",nback,"')&(df_nonTarget$light=='high ipRGC'),]$", SDT)))
      eval(parse(text=paste0("x2 = df_nonTarget[(df_nonTarget$Nback=='",nback,"')&(df_nonTarget$light=='low ipRGC'),]$", SDT)))
    }
    tmp_ttest = getTtestSummary(x1,x2)
    tmp_sig = c(tmp_sig,tmp_ttest$sig)
  }
  
  
  df_SDT <- data.frame(
    sdt = c(paste0("hit(",tmp_sig[1],")"),
            paste0("miss(",tmp_sig[2],")"),
            paste0("FA(",tmp_sig[3],")"),
            paste0("CR(",tmp_sig[4],")")),
    low_ipRGC = c(paste0(round(mean(tmp_low_target$hit),3)," ± ",round(sd(tmp_low_target$hit),3)),
                  paste0(round(mean(tmp_low_target$miss),3)," ± ",round(sd(tmp_low_target$miss),3)),
                  paste0(round(mean(tmp_low$FA)*100,3)," ± ",round(sd(tmp_low$FA)*100,3)),
                  paste0(round(mean(tmp_low$CR)*100,3)," ± ",round(sd(tmp_low$CR)*100,3))),
    high_ipRGC = c(paste0(round(mean(tmp_high_target$hit),3)," ± ",round(sd(tmp_high_target$hit),3)),
                   paste0(round(mean(tmp_high_target$miss),3)," ± ",round(sd(tmp_high_target$miss),3)),
                   paste0(round(mean(tmp_high$FA)*100,3)," ± ",round(sd(tmp_high$FA)*100,3)),
                   paste0(round(mean(tmp_high$CR)*100,3)," ± ",round(sd(tmp_high$CR)*100,3)))
  )
  
  if (nback == "1-back"){
    df_SDT_1back = df_SDT
  }else{
    df_SDT_2back = df_SDT
  }
  
}

config$grCol = c("#222222","#AB004A",rep("#101010",52))


df_pupil = aggregate( Pupil.mm. ~ sub*light*Nback, data = df_pupil, FUN = 'mean')

df = df[order(df$sub,df$light),]
df_pupil = df_pupil[order(df_pupil$sub,df_pupil$light),]

df_response$PD = df_pupil$Pupil.mm.

tmp_df = df[df$hit>0.8,]
p = ggplot(tmp_df, aes(x=PD, y=hit, group=Nback,color=light)) +
  facet_grid(. ~ Nback ) +
  geom_point(size=2, shape=23)+
  geom_smooth(method=lm)


################################ Cr and FA each run ################################ 

# f = list.files(folderName, pattern = "df_run", full.names=T)
# df = fromJSON(file=f[1])


df_targetAll = aggregate( hit ~ sub*Run*light*Nback, data = df_targetAll, FUN = 'mean')

df_targetAll$hit = df_targetAll$hit*100

# anovakun(df,"sABC",long=T, peta=T)

p_all$hit_run = dispLineGraph(df_targetAll,config,"hit",c("Run","light","Nback"))+
  facet_grid( . ~ Nback) 

config$ylim = round(seq(82.5,100,2.5),4)
config$ylim_stride = 0.25
config$xlim = round(seq(1,6,1),4)
config$xlim_stride = 0.5

p_all$hit_run = setEmptyStyle(p_all$hit_run,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    # legend.justification=c(0,1), legend.position=c(1,1),
    # legend.position="right",
    legend.position="none",
    # legend.justification=c(0,1), legend.position=c(0,1),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    # legend.title=element_blank()
  )

p_all$hit_run$size = c(8,6)


```

### desription

To see the effect of light on the task performance of N-back task, we
compared the hit rate between the lighting condition as illustrated in
Figure 2C. We found the main effect of light showing that the the hit
rate under high ipRGC was higher than under low ipRGC
(`r showAnovaSummary(hit_anova,bf_table,2,1)`). There are significant of
interaction between N-back and light condition
(`r showAnovaSummary(hit_anova,bf_table,6,3)`). Post analysis showed
that the higher accuracy under high ipRGC was seen in the 2-back but not
in the 1-back (1-back;`r showTtestSummary(ttest_1back)`,
2-back;`r showTtestSummary(ttest_2back)`). As an effect of working
memory load on accuracy, the hit rate of 1-back task is higher than of
2-back task (`r showAnovaSummary(hit_anova,bf_table,4,2)`). The False
alarm also decreased in the 2-back task under high ipRGC with marginaly
significance (`r showTtestSummary(ttestFA_2back)`). The details of hit,
miss, false alarm and correct rejection are shown in Tables S1.

## Response times

### load data

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_RT <- load_json_dataframe(folderName, "df_RT.json")

```

### code

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}


df_RT_ave = aggregate( RT ~ sub*light*Nback, data = df_RT, FUN = 'mean')

# anovakun(df_ave,"sAB",long=T, peta=T)

# df$light = factor(df$light ,levels = unique(df$light))
# df$sub = factor(df$sub,levels = unique(df$sub))
# df$Nback = factor(df$Nback,levels = unique(df$Nback))
# 
# bf_table = anovaBF(RT ~ light*Nback + sub, data=df, whichRandom = "sub",progress=FALSE)

x1 = df_RT_ave[(df_RT_ave$Nback=="1-back")&(df_RT_ave$light=="high ipRGC"),]$RT
x2 = df_RT_ave[(df_RT_ave$Nback=="1-back")&(df_RT_ave$light=="low ipRGC"),]$RT

ttest_1back = getTtestSummary(x1,x2)
print(getTtestSummary(x1,x2))

x1 = df_RT_ave[(df_RT_ave$Nback=="2-back")&(df_RT_ave$light=="high ipRGC"),]$RT
x2 = df_RT_ave[(df_RT_ave$Nback=="2-back")&(df_RT_ave$light=="low ipRGC"),]$RT

ttest_2back = getTtestSummary(x1,x2)
print(getTtestSummary(x1,x2))

modelList = c(
  "RT ~ light + (1| sub)"
)

estimateAll = NULL
count = 1
for(inback in unique(df_RT$Nback)){
  tmp_df = df_RT[(df_RT$Nback==inback),]
  
  aic_res = NULL
  for( m in modelList){
    eval(parse(text=paste0(" m_",count, " <- lmer(",m,", data=tmp_df)")))
    # sm = summary(model_cand)
    # print(sm)
  }
  count = count+1
}

##################################################################

config$grCol = c("#222222","#AB004A")

p_all$RT = dispLineGraph(df_RT_ave,config,"RT",c("light","light","Nback"))+
  facet_grid(. ~ Nback )


config$ylim = round(seq(500,660,20),4)
config$ylim_stride = 2
config$xlim = round(seq(1,2,1),4)
config$xlim_stride = 0.1

p_all$RT =setEmptyStyle(p_all$RT,config)+
  # scale_x_continuous(breaks = config$xlim)
  theme(
    legend.position="none",
    axis.text.x = element_text(angle = 30, hjust = 1),
  )

p_all$RT$size = c(8,6)

# +
#   geom_signif(data=annotation_df,
#               aes( xmin=start,xmax=end,annotations=label,y_position=y),
#               textsize = 5, size=0.2, tip_length = 0.00,family=fontFamily,manual = TRUE)

# df_RT_sd = df[(df$RT<2000)&(df$hit == 1),]


##################################################################

df_RT_sd = aggregate( RT ~ sub*Run*light*Nback, data = df_RT, FUN = 'sd')

p_all$RT_sd = dispLineGraph(df_RT_sd,config,"RT",c("Run","light","Nback"))+
  facet_grid(. ~ Nback )

# tmp_df_std = aggregate( RT ~ sub*light*Nback, data = tmp_df_std, FUN = 'mean')
# anovakun(df_RT_sd,"sAB",long=T, peta=T)

config$label_x = "Run"
config$label_y = "Standard deviation of RT"

config$ylim = round(seq(80,240,40),4)
config$ylim_stride = 4
config$xlim = round(seq(1,6,1),4)
config$xlim_stride = 0.1

config$label_x = "S.D. of RTs"

p_all$RT_sd = setEmptyStyle(p_all$RT_sd,config)+
  scale_x_continuous(breaks = config$xlim)
theme(
  legend.position="none",
  # axis.text.x = element_text(angle = 30, hjust = 1),
)

p_all$RT_sd$size = c(8,6)


##################################################################

bootstrapRes = list()
set.seed(42)
bootstrap_sample = NULL
N = 10000

for (iNback in unique(df_RT$Nback)){
  
  mean_boot_high <- numeric(N)
  mean_boot_low <- numeric(N)
  
  tmp_df_high = df_RT[(df_RT$light=="high ipRGC")&
                        (df_RT$Nback==iNback),]$RT
  tmp_df_low = df_RT[(df_RT$light=="low ipRGC")&
                       (df_RT$Nback==iNback),]$RT
  
  obs_diff <- mean(tmp_df_high) - mean(tmp_df_low)
  
  obs_std <- sd(tmp_df_high) - sd(tmp_df_low)
  
  combined = c(tmp_df_high,tmp_df_low)
  # hist(combined)
  n1 <- length(tmp_df_high)
  n2 <- length(tmp_df_low)
  
  diffs <- numeric(N)
  diffs2 <- numeric(N)
  # test <- numeric(N)
  diffs_std <- numeric(N)
  
  
  for (k in 1:N){
    
    strap_ind <- sample(1:length(tmp_df_high), replace = TRUE)
    strap_dat <- tmp_df_high[strap_ind]
    mean_boot_high[k] <- mean(strap_dat)
    
    strap_ind <- sample(1:length(tmp_df_low), replace = TRUE)
    strap_dat <- tmp_df_low[strap_ind]
    mean_boot_low[k] <- mean(strap_dat)
    
    sample1 <- sample(combined, size = n1, replace = TRUE)
    sample2 <- sample(combined, size = n2, replace = TRUE)
    
    sample3 <- sample(tmp_df_high, replace = TRUE)
    sample4 <- sample(tmp_df_low, replace = TRUE)
    
    diffs[k] <- mean(sample1) - mean(sample2)
    diffs2[k] <- mean(sample3) - mean(sample4)
    
    diffs_std[k] <- sd(sample1) - sd(sample2)
    
  }
  
  tmp_res = list()
  tmp_res$CI = c(quantile(diffs2, 0.025)[1],quantile(diffs2, 0.975))
  tmp_res$pVal = mean(abs(diffs) >= abs(obs_diff))
  
  tmp_res$pVal_sd = mean(abs(diffs_std) >= abs(obs_std))
  
  if(round(tmp_res$pVal,3)==0){
    tmp_res$pLines = "p < 0.001"
  }else{
    tmp_res$pLines = paste0("$p$ = ",round(tmp_res$pVal,3))
  }
  
  bootstrapRes[[iNback]] = tmp_res
  
  # lower_ci <- quantile(diffs2, 0.025)
  # upper_ci <- quantile(diffs2, 0.975)
  # hist(diffs2)
  # print(lower_ci)
  # print(upper_ci)
  
  # print(hist(diffs))
  
  bootstrap_sample_high = as.data.frame(mean_boot_high)
  bootstrap_sample_high$light = "high"
  bootstrap_sample_high$Nback =iNback
  
  bootstrap_sample_high$RT = bootstrap_sample_high$mean_boot_high
  bootstrap_sample_high$mean_boot_high = NULL
  
  bootstrap_sample_low = as.data.frame(mean_boot_low)
  bootstrap_sample_low$light = "low"
  bootstrap_sample_low$Nback =iNback
  
  bootstrap_sample_low$RT = bootstrap_sample_low$mean_boot_low
  bootstrap_sample_low$mean_boot_low = NULL
  
  bootstrap_sample = rbind(bootstrap_sample, bootstrap_sample_high)
  bootstrap_sample = rbind(bootstrap_sample, bootstrap_sample_low)
  
}


# x1 = bootstrap_sample[(bootstrap_sample$Nback=="1-back")&(bootstrap_sample$light=="high"),]$RT
# x2 = bootstrap_sample[(bootstrap_sample$Nback=="1-back")&(bootstrap_sample$light=="low"),]$RT
# 
# ttest_1back_RT = getTtestSummary(x1,x2)
# 
# x1 = bootstrap_sample[(bootstrap_sample$Nback=="2-back")&(bootstrap_sample$light=="high"),]$RT
# x2 = bootstrap_sample[(bootstrap_sample$Nback=="2-back")&(bootstrap_sample$light=="low"),]$RT
# 
# ttest_2back_RT = getTtestSummary(x1,x2)
# 
# x1 = bootstrap_sample[(bootstrap_sample$Nback=="1-back"),]$RT
# x2 = bootstrap_sample[(bootstrap_sample$Nback=="2-back"),]$RT
# 
# ttest_nback_RT = getTtestSummary(x1,x2)

# p=ggplot(bootstrap_sample, aes(x = RT, color=light)) +
#   # geom_density(aes(fill=light),alpha=0.4)
#   geom_histogram(position = "identity", bins = 50,alpha=0.4)


p_all$RT_bootstrap <- ggplot(bootstrap_sample, aes(x = RT, y = ..density.., fill = light, group=interaction(light,Nback)))+
  # facet_grid(Nback ~ . )+
  geom_histogram(position = "identity", bins = 200, alpha = 0.6)+
  # geom_density(aes(color = light), alpha = 0.6, show.legend = F)+
  scale_fill_manual(values = c("#AB004A","#222222","#AB004A","#222222"))+
  scale_color_manual(values = c("#AB004A","#222222","#AB004A","#222222"))

config$ylim = round(seq(0,0.15,0.025),4)
config$ylim_stride = 0.001
config$xlim = round(seq(500,660,20),4)
config$xlim_stride = 1

p_all$RT_bootstrap = setEmptyStyle(p_all$RT_bootstrap,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    # legend.position="none",
    axis.text.x = element_text(angle = 30, hjust = 1),
  )

p_all$RT_bootstrap$size = c(8,6)

print(bootstrapRes[["2-back"]]$pLines)

# (CI[`r round(ttest_1back_RT$ttest$conf.int[1],3)`, `r round(ttest_1back_RT$ttest$conf.int[2],3)`], 
# `r showTtestSummary(ttest_1back_RT)`; 
# CI[`r round(ttest_2back_RT$ttest$conf.int[1],3)`, `r round(ttest_2back_RT$ttest$conf.int[2],3)`], 
# `r showTtestSummary(ttest_2back_RT)`,respectively).



```

### desription

Response time (RT) was calculated from the stimulus onset to the
participants’ key presses. Linear mixed model analyses were conducted
corresponds to the following formula: $RT \sim Light + (1+|Subject)$. To
statistically assess whether the RTs differed between lighting
conditions, 95% confidence intervals (CI) for the RTs were estimated
with 10000 bootstrap samples. The estimated CIs of RTs between low and
high ipRGC was [`r round(bootstrapRes[["1-back"]]$CI[1],3)`,
`r round(bootstrapRes[["1-back"]]$CI[2],3)`],
`r showLMESummary(m_1,"lightlow ipRGC")` for 1-back and
[`r round(bootstrapRes[["2-back"]]$CI[1],3)`,
`r round(bootstrapRes[["2-back"]]$CI[2],3)`],
`r showLMESummary(m_2,"lightlow ipRGC")` for 2-back shown at top in
Figure2D. The RTs was significantly faster for high ipRGC light for both
1- and 2-back task.

<!-- Although the main effect of light condition did not show the differences of RT (`r showAnovaSummary(forDrawingSigANOVA,bf_table,2,1)`), post analysis showed marginaly significance of faster RTs under high ipRGC in the 1-back but not in the 2-back (1-back;`r showTtestSummary(ttest_1back)`, 2-back;`r showTtestSummary(ttest_2back)`).  -->

## Questionnaire

### load data
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_questionaire  <- load_json_dataframe(folderName, "questionaire.json")
df_questionaire_run  <- load_json_dataframe(folderName, "data_timeCourse_RunAve.json")
df_pupil  <- load_json_dataframe(folderName, "df_targetAll")
df_pupil_timecourse  <- load_json_dataframe(folderName, "data_timeCourse_each.json")

df_questionaire$light = factor( df_questionaire$light ,levels=c("low ipRGC","high ipRGC"))
df_questionaire_run$light = factor( df_questionaire_run$light ,levels=c("low ipRGC","high ipRGC"))
df_pupil$light = factor( df_pupil$light ,levels=c("low ipRGC","high ipRGC"))
df_pupil_timecourse$light = factor( df_pupil_timecourse$light ,levels=c("low ipRGC","high ipRGC"))

df_questionaire_run = df_questionaire_run[order(df_questionaire_run$sub,df_questionaire_run$Run,df_questionaire_run$Nback),]
df_questionaire = df_questionaire[order(df_questionaire$sub,df_questionaire$Run),]

df_pupil_ave = aggregate( Pupil.mm. ~ sub*light*Nback, data = df_pupil_timecourse[df_pupil_timecourse$Time.s.>=0,], FUN = 'mean')
df_pupil_ave$light = factor( df_pupil_ave$light ,levels=c("low ipRGC","high ipRGC"))

df_RT = df_pupil[df_pupil$hit==1,]
df_RT = aggregate( . ~ sub*Run*light*Nback, data = df_RT, FUN = 'mean')

```

### corr sleepiness x fatigue for each sub
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}


tmp_df = df_questionaire[df_questionaire$Task=="Sleepiness",]
tmp_df$ans_Sleepiness = tmp_df$ans_norm
tmp_df$ans_Fatigue = df_questionaire[df_questionaire$Task=="Fatigue",]$ans_norm

tmp_df$Sleepiness <- scale(tmp_df$Sleepiness)[,1]
tmp_df$Fatigue <- scale(tmp_df$Fatigue)[,1]

tmp_df$sub = factor(tmp_df$sub,levels=unique(tmp_df$sub))

p_all$rating_corr = ggplot(tmp_df,aes(x=ans_Sleepiness,
                                      y=ans_Fatigue,
                                      colour = sub,
                                      # group=interaction(light,Run)
                                      # group=interaction(light,sub)
                                      group = sub
))+
  facet_wrap(sub ~ .)+
  stat_smooth(method = "lm", se = FALSE, size = 1)+
  geom_point()

# p_all$rating_corr = ggplot(df,aes(x=Sleepiness,y=Fatigue,colour = light, group=interaction(light,sub)))+
# facet_grid(. ~ Run)+
# facet_wrap(. ~ sub)+
# geom_jitter(width = 0.1, height=0.1)+
# scale_fill_manual(values = c("#AB004A","#222222"))+
# scale_color_manual(values = c("#222222","#AB004A"))

config$ylim = round(seq(0,10,1),4)
config$ylim_stride = 1
config$xlim = round(seq(0,10,1),4)
config$xlim_stride = 1

p_all$rating_corr = setEmptyStyle(p_all$rating_corr,config)+
  scale_x_continuous(breaks = config$xlim)+
  coord_equal()+
  theme(
    legend.justification=c(1,0), legend.position=c(1,0.1),
    legend.title=element_blank()
  )

p_all$rating_corr$size = c(14,6)

```

### sleepiness x fatigue for each run (no run corrected)
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

config$shape=F
config$label_x = "Run"

df_questionaire$ans_plot = df_questionaire$ans_norm
df_questionaire$ans_plot = df_questionaire$ans

p_all$question = dispLineGraph(df_questionaire,config,"ans_plot",c("Run","light","Task"))+
  facet_grid(. ~ Task )

config$ylim = round(seq(2,7,1),4)
config$ylim_stride = 0.1
config$xlim = round(seq(1,6,1),4)
config$xlim_stride = 0.5

p_all$question = setEmptyStyle(p_all$question,config)+
  scale_x_continuous(breaks = config$xlim)+
  theme(
    legend.justification=c(1,0), legend.position=c(1,0.1),
    legend.title=element_blank()
  )

p_all$question$size = c(8,6)


```


### comparison between lighting orders
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

corrAll = NULL
for (iSub in unique(df_questionaire$sub)){
  for (iTask in unique(df_questionaire$Task)){
    # for (iLight in unique(df_questionaire$light)){
    
    x = df_questionaire[
      # (df_questionaire$light==iLight)&
      (df_questionaire$Task==iTask)&
        (df_questionaire$sub == iSub),]$Run
    
    y = df_questionaire[
      # (df_questionaire$light==iLight)&
      (df_questionaire$Task==iTask)&
        (df_questionaire$sub == iSub),]$ans
    
    tmp_df = data.frame(
      sub = iSub,
      corr = cor.test(x,y)[["estimate"]][["cor"]],
      Task = iTask
      # light = iLight
    )
    
    corrAll = rbind(corrAll,tmp_df)
    # }
  }
}

# x = df_questionaire[(df_questionaire$Task=="Fatigue"),]$Run
# y = df_questionaire[(df_questionaire$Task=="Fatigue"),]$ans
# 
# print(cor.test(x,y)[["estimate"]][["cor"]])
# 
# x = df_questionaire[(df_questionaire$Task=="Sleepiness"),]$Run
# y = df_questionaire[(df_questionaire$Task=="Sleepiness"),]$ans
# 
# print(cor.test(x,y)[["estimate"]][["cor"]])

# p_all$corrAll = dispLineGraph(corrAll,config,"corr",c("Task"))


#### make model ####################################################################

df_questionaire$group = "low ipRGC 1st"
for(iSub in sort(unique(df_questionaire$sub))){
  if (df_questionaire[(df_questionaire$sub==iSub)&(df_questionaire$light=="low ipRGC"),]$orderNum[1] == 1){
    df_questionaire[df_questionaire$sub==iSub,]$group = "high ipRGC 1st"
  }
}

modelList = c(
  "ans ~ light * group * Run + (1| sub)"
  # "ans ~ light + (1+Run| sub)"
)

df_questionaire$lightNum = 0
df_questionaire[df_questionaire$light=="high ipRGC",]$lightNum = 1

df_questionaire$groupNum = 0
df_questionaire[df_questionaire$group=="high ipRGC 1st",]$groupNum = 1

df_questionaire$ans_regressout = 0
df_questionaire$regressor = 0
df_questionaire$model = 0

for(mmName in c("Sleepiness","Fatigue")){
  tmp_df = df_questionaire[df_questionaire$Task==mmName,]
  # tmp_df = aggregate( ans ~ sub*lightNum*groupNum*Run, data = tmp_df, FUN = 'mean')
  # print(mmName)
  aic_res = NULL
  for( m in modelList){
    eval(parse(text=paste0(" model_cand <- lmer(",m,", data=tmp_df)")))
    # print(m)
    # summary(model_cand)
    # print(AIC(model_cand))
    
    aic_res = c(aic_res,AIC(model_cand))
  }
  eval(parse(text=paste0(" m_", mmName," <- lmer(",modelList[which.min(aic_res)],", data=tmp_df)")))
  print(eval(parse(text=paste0("summary(m_", mmName,")"))))
  
  # print(eval(parse(text=paste0("anova(lmer(",modelList[which.min(aic_res)],", data=tmp_df))"))))
  
}

modelList = c(
  "ans ~ light + Run + orderNum + (1| sub)"
)


estimateRun = NULL
for(mmName in c("Sleepiness","Fatigue")){
  tmp_df = df_questionaire[df_questionaire$Task==mmName,]
  
  aic_res = NULL
  m <- lmer(modelList, data=tmp_df)
  eval(parse(text=paste0("estimateRun$", mmName,"=m")))
}

#### average ####################################################################

config$shape=F
config$linetype=F
config$label_x = "Run"

p_all$questionBwGroup = dispLineGraph(df_questionaire,config,"ans",c("light","group","Task"))+
  facet_grid(. ~ Task )

config$ylim = round(seq(2,8,1),4)
config$ylim_stride = 0.1
config$xlim = round(seq(1,2,1),4)
config$xlim_stride = 0.5

p_all$questionBwGroup = setEmptyStyle(p_all$questionBwGroup,config)+
  theme(
    legend.position="none",
    # legend.justification=c(0,1), legend.position=c(0,1),
    axis.text.x = element_text(angle = 30, hjust = 1),
  )

p_all$questionBwGroup$size = c(8,6)



```

### sleepiness x fatigue for each run (regressedout run effect)
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_pupil$PD_phasic= df_pupil$Pupil.a.u..

df_pupil_ave = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')
# df_pupil = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'sd')

df_pupil_ave = df_pupil_ave[order(df_pupil_ave$sub,df_pupil_ave$Run,df_pupil_ave$Nback),]
df_RT = df_RT[order(df_RT$sub,df_RT$Run,df_RT$Nback),]

df_pupil_ave$RT = df_RT$RT
df_pupil_ave$Sleepiness = df_questionaire_run$Sleepiness
df_pupil_ave$Fatigue  = df_questionaire_run$Fatigue

df_pupil_ave$lightNum = 0
df_pupil_ave[df_pupil_ave$light=="high ipRGC",]$lightNum = 1

modelList = c(
  "hit ~ lightNum + Sleepiness + Fatigue + (1+Run| sub)"
  # "RT ~ lightNum + Sleepiness + Fatigue + (1 + Run| sub)"
)

### normalized
df_pupil_ave$hit <- scale(df_pupil_ave$hit)[,1]
df_pupil_ave$RT <- scale(df_pupil_ave$RT)[,1]
df_pupil_ave$lightNum <- scale(df_pupil_ave$lightNum)[,1]
df_pupil_ave$Sleepiness <- scale(df_pupil_ave$Sleepiness)[,1]
df_pupil_ave$Fatigue <- scale(df_pupil_ave$Fatigue)[,1]

estimateAll = NULL
for(inback in unique(df_pupil_ave$Nback)){
  
  tmp_df = df_pupil_ave[(df_pupil_ave$Nback==inback),]
  
  model_fits <- map(modelList, ~ {
    model <- lmer(as.formula(.x), data = tmp_df)
    list(formula = .x, model = model, aic = AIC(model), bic = BIC(model))
  })
  
  best_model <- model_fits[[which.min(map_dbl(model_fits, "aic"))]]
  sm <- summary(best_model$model)
  
  terms <- c("Sleepiness", "Fatigue", "lightNum")
  
  coef_df <- extract_coef_info(sm, terms)
  
  coef_df$formula = c(sm$call$formula)
  coef_df$Nback = inback
  
  estimateAll = rbind(estimateAll,coef_df)
  
}

estimateAll[estimateAll$factor=="lightNum",]$factor = "ipRGC"

annotation_df <- NULL
for(inback in unique(estimateAll$Nback)){
  for(iFactor in unique(estimateAll$factor)){
    
    tmp_annotation_df <- data.frame(
      Nback = inback,
      start = iFactor,
      end = iFactor,
      y = 0.3
    )
    pVal = estimateAll[(estimateAll$Nback == inback)&(estimateAll$factor == iFactor),"pVal"]
    if(pVal  < 0.05){
      tmp_annotation_df$label = "*"
    }else if((pVal > 0.05) & (pVal < 0.1)){
      tmp_annotation_df$label = "+"
    }else{
      tmp_annotation_df$label = "n.s."
    }
    annotation_df = rbind(annotation_df,tmp_annotation_df)
  }
}

estimateAll$factor = factor(estimateAll$factor ,levels = c("ipRGC","Sleepiness","Fatigue"))

p_all$weight = ggplot(estimateAll,aes(x=factor,y=Estimate))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = min, ymax = max),
                size = 0.1, width = 0.1,
                position = position_dodge(.1),color="black")+
  facet_grid(. ~ Nback )+
  geom_signif(data=annotation_df,aes(xmin=start,
                                     xmax=end,
                                     annotations=label,y_position=y),
              textsize = 5, size=0.2, tip_length = 0.00,color="black",family=fontFamily,manual = TRUE)

config$ylim = round(seq(-0.3,0.3,0.1),4)
config$ylim_stride = 0.01
config$xlim = round(seq(1,3,1),4)
config$xlim_stride = 0.5
config$label_y = "Weight"

p_all$weight = setEmptyStyle(p_all$weight,config)+
  # scale_x_continuous(breaks = config$xlim)+
  theme(
    # legend.justification=c(0,1), legend.position=c(1,1),
    # legend.position="right",
    legend.position="none",
    # legend.justification=c(0,1), legend.position=c(0,1),
    # axis.text.x = element_text(angle = 30, hjust = 1),
    # legend.title=element_blank()
  )

p_all$weight$size = c(7,5)

##### LMM ###################################################################

modelList = c(
  "RT ~ lightNum + Sleepiness + Fatigue + (1 + Run| sub)"
)


estimateRTAll = NULL
for(inback in unique(df_pupil_ave$Nback)){
  
  tmp_df = df_pupil_ave[(df_pupil_ave$Nback==inback),]
  
  model_fits <- map(modelList, ~ {
    model <- lmer(as.formula(.x), data = tmp_df)
    list(formula = .x, model = model, aic = AIC(model), bic = BIC(model))
  })
  
  best_model <- model_fits[[which.min(map_dbl(model_fits, "aic"))]]
  sm <- summary(best_model$model)
  
  terms <- c("Sleepiness", "Fatigue", "lightNum")
  
  coef_df <- extract_coef_info(sm, terms)
  
  coef_df$formula = c(sm$call$formula)
  coef_df$Nback = inback
  
  estimateRTAll = rbind(estimateRTAll,coef_df)
  
}

estimateRTAll[estimateRTAll$factor=="lightNum",]$factor = "ipRGC"

estimateRTAll$factor = factor(estimateRTAll$factor ,levels = c("ipRGC","Sleepiness","Fatigue"))

annotation_df = NULL

for(inback in unique(estimateRTAll$Nback)){
  for(iFactor in unique(estimateRTAll$factor)){
    
    tmp_annotation_df <- data.frame(
      Nback = inback,
      start = iFactor,
      end = iFactor,
      y = 0.1
    )
    pVal = estimateRTAll[(estimateRTAll$Nback == inback)&(estimateRTAll$factor == iFactor),"pVal"]
    if(pVal  < 0.05){
      tmp_annotation_df$label = "*"
    }else if((pVal > 0.05) & (pVal < 0.1)){
      tmp_annotation_df$label = "+"
    }else{
      tmp_annotation_df$label = "n.s."
    }
    annotation_df = rbind(annotation_df,tmp_annotation_df)
  }
}

p_all$weightRT = ggplot(estimateRTAll,aes(x=factor,y=Estimate))+
  geom_point(size = 4)+
  geom_errorbar(aes(ymin = min, ymax = max),
                size = 0.1, width = 0.1,
                position = position_dodge(.1),color="black")+
  facet_grid(. ~ Nback )+
  geom_signif(data=annotation_df,aes(xmin=start,
                                     xmax=end,
                                     annotations=label,y_position=y),
              textsize = 5, size=0.2, tip_length = 0.00,color="black",family=fontFamily,manual = TRUE)


config$ylim = round(seq(-0.3,0.2,0.1),4)
config$ylim_stride = 0.01
config$xlim = round(seq(1,3,1),4)
config$xlim_stride = 0.5


p_all$weightRT = setEmptyStyle(p_all$weightRT,config) +
  theme(
    legend.position="none",
  )

p_all$weightRT$size = c(7,5)

# and 1st to 2nd block as well (`r showLMESummary(m_Sleepiness,"grouplow ipRGC 1st")`, `r showLMESummary(m_Fatigue,"grouplow ipRGC 1st")`). 

# <!-- We report the fixed effects of following model since the goodness of fit for the model including the order of the session is better than the model with light and run (`r showLMESummary(m_Sleepiness,"lightNum")`,  -->
# <!-- `r showLMESummary(m_Sleepiness,"Run")`). -->
# 
# <!-- We report the fixed effects of following model since the goodness of fit for the model including the order of the session is better than the model with light and run (`r showLMESummary(m_Fatigue,"lightNum")`,  -->
# <!-- `r showLMESummary(m_Fatigue,"Run")`). -->

```

### desription

To test whether the light condition affected participants’ sleepiness
and fatigue, we asked participants to rate their subjective sleepiness
and fatigue on a scale of 0-10. The fixed effects of light, run, and
their interaction model including block order are reported here; we
fitted the rating scores with light, run, and block order as
within-subject factors and subject as a between-subject factor. The
block order refers to whether the high ipRGC block or low ipRGC block
was performed in the first block. The scores were negatively affected by
the light condition, indicating that the high ipRGC light contributed to
a lower subjective score for both sleepiness and fatigue
(sleepiness: `r showLMESummary(m_Sleepiness,"lighthigh ipRGC")`;
fatigue: `r showLMESummary(m_Fatigue,"lighthigh ipRGC")`).

To examine whether pupil size could be attributed to variations in subjective fatigue and sleepiness, we computed correlations between pupil size and these subjective ratings. As shown in Supplementary Figure S2, we observed a significant correlation between pupil size and fatigue ratings, but not with sleepiness. Additionally, we confirmed that the degree of pupil constriction under high-ipRGC light was not predictive of the individual brightness adjustment values in the brightness-matching experiment.

We fitted the rating scores with run and participants as a random effect
using a linear mixed model, showing that the subjective sleepiness and
fatigue scores increased significantly with an increasing effect of
time-on-task
(sleepiness: `r showLMESummary(estimateRun$Sleepiness,"Run")`;
fatigue: `r showLMESummary(estimateRun$Fatigue,"Run")`).

<!-- ($t$=`r round(estimateAll[(estimateAll$factor=="ipRGC")&(estimateAll$Nback=="2-back"),]$t,3)`, -->
<!-- $p$=`r round(estimateAll[(estimateAll$factor=="ipRGC")&(estimateAll$Nback=="2-back"),]$pVal,3)`, -->
<!-- $d_z$=`r estimateAll[(estimateAll$factor=="ipRGC")&(estimateAll$Nback=="2-back"),]$cohend`; -->
<!-- $t$=`r round(estimateAll[(estimateAll$factor=="Fatigue")&(estimateAll$Nback=="2-back"),]$t,3)`, -->
<!-- $p$=`r round(estimateAll[(estimateAll$factor=="Fatigue")&(estimateAll$Nback=="2-back"),]$pVal,3)`, -->
<!-- $d_z$=`r estimateAll[(estimateAll$factor=="Fatigue")&(estimateAll$Nback=="2-back"),]$cohend`). -->

$Rating \sim Light + Session + Run + (1|Subject)$

$Hit\ rate \sim Light + Sleepiness + Fatigue + (1+Run|Subject)$

### pupil time course and phasic response

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# df_pupil_ave = aggregate( Pupil.mm. ~ sub*light*Nback, data = df_pupil_timecourse[df_pupil_timecourse$Time.s.>=0,], FUN = 'mean')
# df_pupil_ave$light = factor( df_pupil_ave$light ,levels=c("low ipRGC","high ipRGC"))
# 
# anovakun(df_pupil_ave,"sAB",long=T, peta=T)
# 
# df_pupil_ave$light = factor(df_pupil_ave$light ,levels = unique(df_pupil_ave$light))
# df_pupil_ave$sub = factor(df_pupil_ave$sub,levels = unique(df_pupil_ave$sub))
# df_pupil_ave$Nback = factor(df_pupil_ave$Nback,levels = unique(df_pupil_ave$Nback))
# 
# bf_table = anovaBF(Pupil.mm. ~ light*Nback + sub, data=df, whichRandom = "sub",progress=FALSE)
# 
# x1 = df_pupil_ave[(df_pupil_ave$Nback=="1-back")&(df_pupil_ave$light=="high ipRGC"),]$Pupil.mm.
# x2 = df_pupil_ave[(df_pupil_ave$Nback=="1-back")&(df_pupil_ave$light=="low ipRGC"),]$Pupil.mm.
# 
# ttest_1back = getTtestSummary(x1,x2)
# 
# x1 = df_pupil_ave[(df_pupil_ave$Nback=="2-back")&(df_pupil_ave$light=="high ipRGC"),]$Pupil.mm.
# x2 = df_pupil_ave[(df_pupil_ave$Nback=="2-back")&(df_pupil_ave$light=="low ipRGC"),]$Pupil.mm.
# 
# ttest_2back = getTtestSummary(x1,x2)
# 
# annotation_df$label = c(ttest_1back$sig,ttest_2back$sig)
# annotation_df$y=0.03
# 
# config <- list(lim_x = c(min(df_pupil$Time.s.),max(df_pupil$Time.s.)),
#                lim_y = c(-0.05,0.05),
#                alpha = 0.1,
#                stride = 0.1,
#                label_x = "Time [sec]",
#                label_y = "Pupil size[mm]",
#                title = "",
#                linetype = T,
#                grCol = c("#222222","#AB004A"),
#                shape = F
# )
# 
# df_pupil_timecourse$data_x = df_pupil_timecourse$Time.s.
# p_all$pupilTimeCourse <- disp(df_pupil_timecourse,config,"Pupil.mm.",1,c("light","Nback")) +
#   # facet_grid(Run ~ .)+
#   theme(
#     # legend.justification=c(0,1), legend.position=c(0,1),
#     # legend.justification=c(0,1), legend.position=c(1,1)
#     legend.position="right",
#     # legend.position="none",
#   )
# 
# config$ylim = round(seq(-0.06,0.06,0.02),4)
# config$ylim_stride = 0.01
# config$xlim = round(seq(-0.2,1.6,0.2),2)
# config$xlim_stride = 0.05
# 
# config$label_x = ""
# p_all$pupilTimeCourse = setEmptyStyle(p_all$pupilTimeCourse,config)+
#   scale_x_continuous(breaks = config$xlim)
# 
# p_all$pupilTimeCourse$size = c(10,6)
# 
# 
# ############ phasic ave ############
# 
# 
# p_all$pupil_phasic_ave = dispLineGraph(df_pupil_ave,config,"Pupil.mm.",c("light","light","Nback"))+
#   facet_grid(. ~ Nback)
# # +
# #   geom_signif(data=annotation_df,
# #               aes( xmin=start,xmax=end,annotations=label,y_position=y),
# #               textsize = 5, size=0.2, tip_length = 0.00,family=fontFamily,manual = TRUE)
# 
# 
# # config$ylim = round(seq(0.03,0.06,0.01),4)
# config$ylim = round(seq(0,0.04,0.01),4)
# config$ylim_stride = 0.01
# config$xlim = round(seq(1,2,1),4)
# config$xlim_stride = 0.5
# 
# p_all$pupil_phasic_ave = setEmptyStyle(p_all$pupil_phasic_ave,config)+
#   theme(
#     # legend.justification=c(0,1), legend.position=c(0,1),
#     # legend.justification=c(0,1), legend.position=c(1,1),
#     # legend.position="right",
#     # legend.title=element_blank(),
#     legend.position="none",
#     axis.text.x = element_text(angle = 30, hjust = 1)
#   )
# 
# p_all$pupil_phasic_ave$size = c(6,6)

```

### regress out the effect of time-on-task

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

df_pupil_ave = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')

df_pupil_ave <- df_pupil_ave %>%
  arrange(sub, light, Run, Nback) %>%
  mutate(
    Sleepiness = df_questionaire_run %>%
      arrange(sub, light, Run, Nback) %>%
      pull(Sleepiness),
    Fatigue = df_questionaire_run %>%
      arrange(sub, light, Run, Nback) %>%
      pull(Fatigue)
  )

df_pupil_ave$lightNum = 0
df_pupil_ave[df_pupil_ave$light=="high ipRGC",]$lightNum = 1

inback = "2-back"

# for(mmName in c("Sleepiness","Fatigue","lightNum")){
for(mmName in c("Sleepiness","Fatigue")){
  
  eval(parse(text=paste0("df_pupil_ave$model_",mmName,"=0")))
  
  for(inback in unique(df_pupil_ave$Nback)){
    
    tmp_df = df_pupil_ave[(df_pupil_ave$Nback==inback),]
    
    eval(parse(text=paste0("modelList = '",mmName," ~ Run + (1+Run| sub)'")))
    # eval(parse(text=paste0("modelList = '",mmName," ~ lightNum + Run + (1| sub)'")))
    # eval(parse(text=paste0("modelList = '",mmName," ~ lightNum + (1+Run| sub)'")))
    # eval(parse(text=paste0("modelList = ' hit ~ ",mmName," + (1+Run| sub)'")))
    
    eval(parse(text=paste0(" m <- lmer(", modelList, ", data = tmp_df)")))
    # sm = summary(m)
    
    tmp_df$model = 0
    tmp_df$model = tmp_df$model + fixef(m)["(Intercept)"]
    tmp_df$model = tmp_df$model + tmp_df$Run * fixef(m)["Run"]
    # tmp_df$model = tmp_df$model + tmp_df$lightNum * fixef(m)["lightNum"]
    
    c = 1
    for(iSub in unique(tmp_df$sub)){
      
      tmp_df[(tmp_df$sub == iSub),]$model = tmp_df[(tmp_df$sub == iSub),]$model + ranef(m)[["sub"]][["(Intercept)"]][c]
      tmp_df[(tmp_df$sub == iSub),]$model = tmp_df[(tmp_df$sub == iSub),]$model + ranef(m)[["sub"]][["Run"]][c]*tmp_df[(tmp_df$sub == iSub),]$Run
      
      # eval(parse(text=paste0("tmp_df[(tmp_df$sub == iSub),]$model = tmp_df[(tmp_df$sub == iSub),]$",mmName," - ranef(m)[['sub']][['Run']][c]*tmp_df[(tmp_df$sub == iSub),]$Run")))
      
      c = c + 1
    }
    
    eval(parse(text=paste0(" df_pupil_ave[(df_pupil_ave$Nback==inback),]$model_",mmName," = tmp_df$model")))
    
  }
}

df_pupil_ave$model_Sleepiness = df_pupil_ave$Sleepiness - df_pupil_ave$model_Sleepiness
df_pupil_ave$model_Fatigue = df_pupil_ave$Fatigue - df_pupil_ave$model_Fatigue

# tmp_df2 = aggregate( . ~ sub*light*Nback, data = tmp_df, FUN = 'mean')
# 
# p = NULL
# 
# config$xlim = round(seq(1,2,1),4)
# config$xlim_stride = 0.1
# config$ylim = round(seq(3.8,5.6,0.1),4)
# config$ylim_stride = 0.01
# 
# p$p1 = dispLineGraph(tmp_df2,config,"model_Sleepiness",c("light"))
# p$p1 = setEmptyStyle(p$p1,config)
# 
# p$p2 = dispLineGraph(tmp_df2,config,"Sleepiness",c("light"))
# p$p2 = setEmptyStyle(p$p2,config)
# p$p3 = dispLineGraph(tmp_df2,config,"model_Fatigue",c("light"))
# p$p3 = setEmptyStyle(p$p3,config)
# 
# 
# p$p4 = dispLineGraph(tmp_df2,config,"Fatigue",c("light"))
# p$p4 = setEmptyStyle(p$p4,config)
# 
# p = combineGraphs2(c("p1","p2","p3","p4"),p,c(1,4))

tmp_df = aggregate( . ~ sub*Run*light*Nback, data = df_pupil_ave, FUN = 'mean')

p_all2 = NULL
config$xlim = round(seq(1,6,1),4)
config$xlim_stride = 0.1
config$ylim = round(seq(-0.8,0.8,0.2),4)
config$ylim_stride = 0.02

config$label_y = "Sleepiness (Run effect was regress out)"
config$label_x = "Run"

p_all$model_Sleepiness = dispLineGraph(tmp_df,config,"model_Sleepiness",c("Run","light"))
p_all$model_Sleepiness = setEmptyStyle(p_all$model_Sleepiness,config)+
  scale_x_continuous(breaks = config$xlim)

config$label_y = "Fatigue (Run effect was regress out)"
p_all$model_Fatigue = dispLineGraph(tmp_df,config,"model_Fatigue",c("Run","light"))
p_all$model_Fatigue = setEmptyStyle(p_all$model_Fatigue,config)+
  scale_x_continuous(breaks = config$xlim)

p_all$model_Sleepiness$size=c(8,6)
p_all$model_Fatigue$size=c(8,6)

# p_all2$run_fatigue = ggplot(tmp_df,aes(x=model_Fatigue,y=model_Sleepiness,
#                                        group=interaction(light,sub),color=interaction(light,sub)))+
#   geom_point()+
#   facet_wrap(. ~ sub )+
#   stat_smooth(method = "lm", se = FALSE, size = 1)


# p = NULL
# p$p3 = dispLineGraph(tmp_df,config,"Sleepiness",c("Run","light"))
# p$p4 = dispLineGraph(tmp_df,config,"Fatigue",c("Run","light"))
# p = combineGraphs2(c("p3","p4"),p,c(1,2))

##########################################################################

```

## Phasic pupil response

<!-- `r showAnovaSummary(forDrawingSigANOVA,bf_table,2,1)` -->

<!-- `r showAnovaSummary(forDrawingSigANOVA,bf_table,4,2)` -->

<!-- `r showAnovaSummary(forDrawingSigANOVA,bf_table,6,3)` -->

```{r, message=FALSE, warning=FALSE, echo=FALSE}

p_all$combinedFigs = combineGraphs2(c("pupil_ave","hit","RT_bootstrap"),p_all,c(1,3))
p_all$combinedFigs$size=c(15,5)

p_all$combinedFigs2 = combineGraphs2(c("question","weight"),p_all,c(1,2))
p_all$combinedFigs2$size=c(10,5)

# ```{r, message=FALSE, warning=FALSE, echo=FALSE, results='asis'}
# print(kable(df_SDT_1back, format = "markdown", digits = 3, row.names = NA,caption = "test"))
# ```
```

# Supplementary Figure
## Table for hit, miss, FA and CR

### 1-back

`r  kable(df_SDT_1back, format = "markdown", digits = 3, row.names = NA)`
### 2-back
`r  kable(df_SDT_2back, format = "markdown", digits = 3, row.names = NA)`

<!-- ## Table for Questionare -->

<!-- `r kable(summary(m_Sleepiness)$coefficients, format = "markdown", digits = 3, row.names = NA)` -->

<!-- `r kable(summary(m_Fatigue)$coefficients, format = "markdown", digits = 3, row.names = NA)` -->


### corr Pupil x (sleepiness,fatigue)
```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

tmp_df = df_pupil_ave
tmp_df$sub = factor( tmp_df$sub ,levels=unique(tmp_df$sub))

config$label_x = "Pupil size[mm]"

config$xlim = round(seq(2,4,0.5),4)
config$xlim_stride = 0.05
config$ylim = round(seq(-5,5,1),4)
config$ylim_stride = 0.1

estimate_corr = NULL
for(mmName in c("Sleepiness","Fatigue")){
  
  config$label_y = paste0(mmName,"\n(Run effect was regress out)")
  eval(parse(text=paste0("tmp_df$data_y=tmp_df$model_",mmName)))
  
  p = ggplot(tmp_df,aes(x=BP, 
                        y=data_y))+
    geom_smooth(method="lm",fomula='y~x',se = FALSE)+
    geom_point(aes(shape=light,
                   group=sub,
                   colour = sub))+
    xlab(config$label_x) + ylab(config$label_y)
  
  p = setEmptyStyle(p,config)
  
  eval(parse(text=paste0("p_all$pupil_",mmName,"_corr=p")))
  
  model = paste0("model_",mmName,"~BP+ (1 | sub)")
  
  m <- lmer(model, data = tmp_df)
  
  eval(parse(text=paste0("estimate_corr$",mmName," = m")))
  
}

tmp_df = df_pupil_ave
tmp_df = aggregate( . ~ sub*light*Nback, data = tmp_df, FUN = 'mean')
tmp_df$BP = tmp_df[tmp_df$light == "high ipRGC",]$BP - tmp_df[tmp_df$light == "low ipRGC",]$BP
tmp_df = tmp_df[(tmp_df$light == "high ipRGC")&(tmp_df$Nback == "2-back"),]

tmp_df$brightness = 0
for(iSub in unique(tmp_df$sub)){
  tmp_df[tmp_df$sub == iSub,]$brightness = df_brightness_ave[df_brightness_ave$sub == iSub,]$Y/df_brightness_ave[df_brightness_ave$sub == iSub,]$ipRGC_Y*100
}

tmp_df$sub = factor( tmp_df$sub ,levels=unique(tmp_df$sub))


p_all$corr_brightness_pupil = ggplot(tmp_df,aes(x=BP, 
                                                y=brightness))+
  geom_smooth(method="lm",fomula='y~x',se = FALSE)+
  geom_point(aes(colour = sub),size = 4)+
  xlab("Diff. btw. ipRGC+ - ipRGC-") + ylab("Brightness")

config$ylim = round(seq(80,160,20),4)
config$ylim_stride = 2
config$xlim = round(seq(-0.8,0.2,0.2),4)
config$xlim_stride = 0.02

p_all$corr_brightness_pupil = setEmptyStyle(p_all$corr_brightness_pupil,config)+
  scale_x_continuous(breaks = config$xlim)

model = "brightness ~ BP"
m <- lm(model, data = tmp_df)

model_summary = summary(m)
if(round(summary(m)$coefficients["BP","Pr(>|t|)"],3)==0){
  pLines = "$p$ < 0.001"
}else{
  pLines = paste0("$p$=",round(model_summary$coefficients["BP","Pr(>|t|)"],3))
}

s = paste0("$t$(",length(unique(tmp_df$sub))-1,") = ", 
           round(model_summary$coefficients["BP","t value"],3),
           ", ", pLines,
           ", $d_z$ = ", abs(round(t_to_d(t = model_summary$coefficients["BP","t value"], 
                                          df_error = length(unique(tmp_df$sub))-1)$d,3))
)

p_all$corr_brightness_pupil$size=c(8,6)


p_all$combinedFigs3 = combineGraphs2(c("pupil_Fatigue_corr",
                                       "pupil_Sleepiness_corr",
                                       "corr_brightness_pupil"),p_all,c(1,3))
p_all$combinedFigs3$size=c(30,7)



```

### description
To examine whether pupil size could be attributed to variations in subjective fatigue and sleepiness, we computed correlations between pupil size and these subjective ratings. A linear mixed-effects model was used, with pupil size as within-subject factors and subject as a between-subject factor, following the equation: Rating∼pupil size+(1|Subject). We found the fatigue ratings, but not sleepiness ratings, were significantly correlated with pupil size 
(fatigue: `r showLMESummary(estimate_corr$Fatigue,"BP")`; sleepiness: `r showLMESummary(estimate_corr$Sleepiness,"BP")`). 

In addition, brightness adjustment values (i.e., how much brighter the high-ipRGC light appeared) ) could not be explained by pupil size 
(`r s`). 
One possible interpretation is that distinct ipRGC subtypes contribute to different functional outcomes[1,2]. For example, M1-type ipRGCs, which primarily project to non-image-forming targets such as the SCN and OPN, may be more directly involved in pupil size. In contrast, non-M1 subtypes are known to project to image-forming regions such as the LGN and are implicated in visuocognitive processing such as brightness enhancement.

# Path analysis

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# df_pupil["Light"] = 1
# df_pupil[df_pupil["light"]=="low ipRGC",]["Light"] = 0
# tmp_data = df_pupil
# [df_pupil["Nback"]=="2-back",]

tmp_df2 = aggregate( . ~ sub*Run*light*Nback, data = df_pupil_ave, FUN = 'mean')
# tmp_df2 = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')
# tmp_df2 = tmp_df[(tmp_df$Nback == "2-back"),]

model <- '
 hit ~ lightNum
  hit ~ model_Sleepiness
  hit ~ model_Fatigue
  model_Sleepiness ~ lightNum
  model_Fatigue ~ lightNum
  model_Sleepiness ~~ model_Fatigue
'

fit <- sem(model, data = tmp_df2)

fit_sm = summary(fit, fit.measures = TRUE, standardized = TRUE)

path_table = as.data.frame(fit_sm[["pe"]])

table_light = path_table[(path_table$rhs == "lightNum")&(path_table$op == "~"),]
table_hit = path_table[(path_table$lhs == "hit")&(path_table$op == "~"),]

m <- matrix(NA, 3, 3)
m[1, 2] <- "lightNum"
m[2, 2] <- "hit"
m[3, 1] <- "model_Sleepiness"
m[3, 3] <- "model_Fatigue"

p = semPaths(fit, 
             # rotation = 2,
             what = "Est",
             # what = "Std",
             # what = "paths",
             edge.label.cex = 1.2,
             # layout = "tree2",
             edge.width = 0.3,
             fade = FALSE,
             style = "ram", 
             residuals = F,
             nCharNodes = 0,
             curvePivot = TRUE,
             optimizeLatRes = TRUE,
             intercepts = FALSE,
             layout = m
)

p_all$p_pa2 <- mark_sig(p, fit)

# plot(p_all$p_pa2)
p_all$p_pa2$size = c(4,3)


model <- '
  hit ~ lightNum+model_Sleepiness+model_Fatigue+BP
  model_Sleepiness ~ lightNum+BP
  model_Fatigue ~ lightNum+BP
  model_Sleepiness ~~ model_Fatigue
  BP ~ lightNum
'

m <- matrix(NA, 5, 3)
m[1, 3] <- "lightNum"
m[2, 3] <- "BP"
m[3, 1] <- "hit"
m[3, 3] <- "model_Sleepiness"
m[4, 3] <- "model_Fatigue"

fit <- sem(model, data = tmp_df2)
fit_sm = summary(fit, fit.measures = TRUE, standardized = TRUE)

semPaths(fit,
         what = "Est",
         edge.label.cex = 1.2,
         # layout = "tree2",
         edge.width = 0.3,
         fade = FALSE,
         style = "ram", 
         residuals = F,
         nCharNodes = 0,
         curvePivot = TRUE,
         optimizeLatRes = TRUE,
         intercepts = FALSE,
         layout = m
)

p = semPaths(fit, 
             # rotation = 2,
             what = "Est",
             # what = "Std",
             # what = "paths",
             edge.label.cex = 1.2,
             # layout = "tree2",
             edge.width = 0.3,
             fade = FALSE,
             style = "ram", 
             residuals = F,
             nCharNodes = 0,
             curvePivot = TRUE,
             optimizeLatRes = TRUE,
             intercepts = FALSE,
             layout = m
)
parameterEstimates(fit, standardized = FALSE)
p_all$p_pa3 <- mark_sig(p, fit)

# plot(p_all$p_pa3)
p_all$p_pa3$size = c(4,3)

```

### desription

Using the coefficient of the model, we regressed out the time-on-task
effect from the rating scores as shown in Figure 3A. To determine how
the light condition, the hit rate, sleepiness, and fatigue affected each
other, we performed a mediation analysis as shown in Figure 3B. We found
the light condition significantly affected hit rate, sleepiness, and
fatigue 
(hit rate:$\beta$ = `r round(table_light[table_light$lhs=="hit",]$std.all,3)`, 
$p$ = `r round(table_light[table_light$lhs=="hit",]$pvalue,3)`, 
$d_z$ = `r abs(round(z_to_d(z=table_light[table_light$lhs=="hit",]$z,n=nrow(tmp_df2))$d,3))`;
sleepiness: $\beta$ = `r round(table_light[table_light$lhs=="model_Sleepiness",]$std.all,3)`, 
$p$ = `r round(table_light[table_light$lhs=="model_Sleepiness",]$pvalue,3)`, 
$d_z$ = `r abs(round(z_to_d(z=table_light[table_light$lhs=="model_Sleepiness",]$z,n=nrow(tmp_df2))$d,3))`;
fatigue: $\beta$ = `r round(table_light[table_light$lhs=="model_Fatigue",]$std.all,3)`, 
$p$ = `r round(table_light[table_light$lhs=="model_Fatigue",]$pvalue,3)`, 
$d_z$ = `r abs(round(z_to_d(z=table_light[table_light$lhs=="model_Fatigue",]$z,n=nrow(tmp_df2))$d,3))`). 
Although sleepiness negatively affected the hit rate with a weak effect (i.e., lower sleepiness improved the hit rate), we did not find strong evidence that the sleepiness and fatigue rating can explain the hit rate 
(sleepiness: $\beta$ = `r round(table_hit[table_hit$rhs=="model_Sleepiness",]$std.all,3)`, 
$p$ = `r round(table_hit[table_hit$rhs=="model_Sleepiness",]$pvalue,3)`, 
$d_z$ = `r abs(round(z_to_d(z=table_hit[table_hit$rhs=="model_Sleepiness",]$z,n=nrow(tmp_df2))$d,3))`;
fatigue: $\beta$ = `r round(table_hit[table_hit$rhs=="model_Fatigue",]$std.all,3)`, 
$p$ = `r round(table_hit[table_hit$rhs=="model_Fatigue",]$pvalue,3)`, 
$d_z$ = `r abs(round(z_to_d(z=table_hit[table_hit$rhs=="model_Fatigue",]$z,n=nrow(tmp_df2))$d,3))`
)

## plot model sleepiness and fatigue

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

p_all$regressout_sleepiness_fatigue = combineGraphs2(c("model_Sleepiness","model_Fatigue"),p_all,c(1,2))
p_all$regressout_sleepiness_fatigue$size=c(15,6)

summary_fit <- parameterEstimates(fit, standardized = FALSE)

equations <- list()

regression_params <- subset(summary_fit, op == "~")

for (dep_var in unique(regression_params$lhs)) {
  terms <- subset(regression_params, lhs == dep_var)
  equation <- paste(dep_var, "~",
                    paste0(round(terms$est,4), " * ", terms$rhs, collapse = " + "))
  
  equations[[dep_var]] <- equation
}

# fit <- sem(model, data = tmp_df2, se = "bootstrap", bootstrap = 10000)
# 
# std_solution_boot <- standardizedSolution(fit)
# print(std_solution_boot)

##########################################################################

# f = list.files(folderName, pattern = "data_timeCourse_ave.json", full.names=T)
# df_pupil = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_pupil)){
#   df_pupil[[iName]] = unlist(df_pupil[[iName]])
# }
# df_pupil = as.data.frame(df_pupil)
# 
# df_pupil = aggregate( Pupil.mm. ~ sub*light, data = df_pupil, FUN = 'mean')
# df_pupil$light = factor( df_pupil$light ,levels=c("low ipRGC","high ipRGC"))
# 
# df_pupil = df_pupil[order(df_pupil$sub,df_pupil$light),]
# 
# tmp_df$PD = df_pupil$Pupil.mm.
# 
# modelList = c(
#   # "ans ~ light + Run + (1 | sub)",
#   # "ans ~ light + group + Run + (1 | sub)",
#   # "ans ~ light + Run + (1 + group| sub)",
#   # "RT ~ light + group + Sleepiness + Fatigue + (1| sub)",
#   # "hit ~ light + group + Sleepiness + Fatigue + (1| sub)",
#   # "hit ~ PD + light + group + Sleepiness + Fatigue + (1| sub)",
#   # "hit ~ PD + light  + Sleepiness + Fatigue + (1| sub)",
#   # "hit ~ PD + (1| sub)",
#   # "hit ~ PD + light + (1| sub)",
#   "hit ~ Sleepiness + Fatigue + (1+group| sub)"
#   # "hit ~ PD + light  + Sleepiness + Fatigue + (1| sub)"
# )
# 
# aic_res = NULL
# for( m in modelList){
#   eval(parse(text=paste0(" model_cand <- lmer(",m,", data=tmp_df)")))
#   print(summary(model_cand))
#   print(AIC(model_cand))
#   # fixef(model_cand)
#   
#   aic_res = c(aic_res,AIC(model_cand))
#   # eval(parse(text=paste0(" m <- lmer(",modelList[which.min(aic_res)],", data=tmp_df)")))
#   # print(eval(parse(text=paste0("summary(mmodel_cand)"))))
# }

# ggplot(tmp_df,aes(x=Fatigue,y=hit,color=sub,shape=group,group=sub))+
#   geom_point()+
#   geom_

############



#### average ####################################################################

# f = list.files(folderName, pattern = "df_target_mean.json", full.names=T)
# df_hit = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_hit)){
#   df_hit[[iName]] = unlist(df_hit[[iName]])
# }
# df_hit = as.data.frame(df_hit)
# 
# tmp_df_hit = df_hit[df_hit$Nback=="2-back",]
# tmp_df_hit$light = factor( tmp_df_hit$light ,levels=c("low ipRGC","high ipRGC"))
# 
# tmp_df_hit <- tmp_df_hit[order(tmp_df_hit$sub,tmp_df_hit$light),]
# 
# tmp_df = aggregate( ans ~ sub*light*group, data = df[df$Task=="Sleepiness",], FUN = 'mean')
# tmp_df_Fatigue = aggregate( ans ~ sub*light*group, data = df[df$Task=="Fatigue",], FUN = 'mean')
# 
# tmp_df$Sleepiness = tmp_df$ans
# tmp_df$Fatigue = tmp_df_Fatigue$ans
# 
# tmp_df <- tmp_df[order(tmp_df$sub,tmp_df$light),]
# 
# tmp_df$hit = tmp_df_hit$hit
# tmp_df$RT = tmp_df_hit$RT
# tmp_df$pupil = tmp_df_hit$Pupil.a.u..

```

### corr

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# df_pupil = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')
# # df_questionaire_run = aggregate( . ~ sub*Run*light*Nback, data = df_questionaire_run, FUN = 'mean')
# 
# df_pupil = df_pupil[order(df_pupil$sub,df_pupil$Run,df_pupil$Nback),]
# df_questionaire_run = df_questionaire_run[order(df_questionaire_run$sub,df_questionaire_run$Run,df_questionaire_run$Nback),]
# 
# df_pupil$Sleepiness = df_questionaire_run$Sleepiness
# df_pupil$Fatigue  = df_questionaire_run$Fatigue
# 
# tmp_plot = df_pupil[df_pupil["Nback"]=="2-back",]
# 
# df_pupil$sub = factor(df_pupil$sub,levels=unique(df_pupil$sub))
# 
# m = lmer(hit ~ Fatigue + Run + (1|sub), data=df_pupil)
# summary(m)
# 
# m = lmer(hit ~ Sleepiness + Run + (1|sub), data=df_pupil)
# summary(m)
# 
# m = lmer(Fatigue ~ light + (1+Run|sub), data=df_pupil)
# summary(m)
# 
# m = lmer(Sleepiness ~ light + (1+Run|sub), data=df_pupil)
# summary(m)
# 
# config$ylim = round(seq(0.5,1,0.1),4)
# config$ylim_stride = 0.01
# config$xlim = round(seq(0,10,1),4)
# config$xlim_stride = 0.5
# 
# p_all$hit_fatigue = ggplot(df_pupil,aes(x=Fatigue,y=hit
#                                         # group=sub,color=sub
#                                         ))+
#   # facet_wrap(. ~ Nback )+
#   geom_point()+
#   stat_smooth(method = "lm", se = FALSE, size = 1)
# 
# p_all$hit_fatigue = setEmptyStyle(p_all$hit_fatigue,config)+
#   scale_x_continuous(breaks = config$xlim)+
#   theme(
#     legend.position="none"
#     # axis.text.x = element_text(angle = 30, hjust = 1)
#   )
# 
# p_all$hit_fatigue$size=c(4,6) 
# 
# p_all$hit_sleepiness = ggplot(df_pupil,aes(x=Sleepiness,
#                                            y=hit
#                                            # group=sub,color=sub
#                                            ))+
#   # facet_wrap(. ~ Nback )+
#   geom_point()+
#   stat_smooth(method = "lm", se = FALSE, size = 1)
# 
# p_all$hit_sleepiness = setEmptyStyle(p_all$hit_sleepiness,config)+
#   scale_x_continuous(breaks = config$xlim)+
#   theme(
#     legend.position="none"
#     # axis.text.x = element_text(angle = 30, hjust = 1)
#   )
# 
# p_all$hit_sleepiness$size=c(4,6) 
# 
# 
# config$ylim = round(seq(0,10,1),4)
# config$ylim_stride = 0.5
# 
# p_all$sleepiness_fatigue = ggplot(df_pupil,aes(x=Sleepiness,y=Fatigue))+
#   # facet_wrap(. ~ Nback )+
#   geom_point()+
#   stat_smooth(method = "lm", se = FALSE, size = 1)
# 
# p_all$sleepiness_fatigue = setEmptyStyle(p_all$sleepiness_fatigue,config)+
#   scale_x_continuous(breaks = config$xlim)+
#   theme(
#     legend.position="none"
#     # axis.text.x = element_text(angle = 30, hjust = 1)
#   )
# 
# p_all$combinedFigs3 = combineGraphs2(c("hit_fatigue","hit_sleepiness","sleepiness_fatigue"),
#                                      p_all,c(1,3))
# p_all$combinedFigs3$size=c(12,4)
# 
# 
# 
# p_all$run_fatigue = ggplot(df_pupil,aes(x=Run,y=Fatigue,group=sub,color=sub))+
#   geom_point()+
#   stat_smooth(method = "lm", se = FALSE, size = 1)
# 
# p_all$run_sleepiness = ggplot(df_pupil,aes(x=Run,y=Sleepiness,group=sub,color=sub))+
#   geom_point()+
#   stat_smooth(method = "lm", se = FALSE, size = 1)
# 
# p = combineGraphs2(c("run_fatigue","run_sleepiness"),
#                                      p_all,c(1,2))
# 

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# f = list.files(folderName, pattern = "questionaire.json", full.names=T)
# df = fromJSON(file=f[1])
# 
# for(iName in 1:length(df)){
#   df[[iName]] = unlist(df[[iName]])
# }
# df = as.data.frame(df)
# 
# f = list.files(folderName, pattern = "data_timeCourse_RunAve.json", full.names=T)
# df2 = fromJSON(file=f[1])
# 
# for(iName in 1:length(df2)){
#   df2[[iName]] = unlist(df2[[iName]])
# }
# 
# df2 = as.data.frame(df2)
# df2 = df2[order(df2$sub,df2$Run,df2$Nback),]
# df = df[order(df$sub,df$Run),]
# 
# f = list.files(folderName, pattern = "df_targetAll", full.names=T)
# df_pupil = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_pupil)){
#   df_pupil[[iName]] = unlist(df_pupil[[iName]])
# }
# df_pupil = as.data.frame(df_pupil)
# 
# df_RT = df_pupil[df_pupil$hit==1,]
# df_RT = aggregate( . ~ sub*Run*light*Nback, data = df_RT, FUN = 'mean')
# 
# df_pupil$PD_phasic= df_pupil$Pupil.a.u..
# 
# df_pupil = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')
# # df_pupil = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'sd')
# 
# df_pupil = df_pupil[order(df_pupil$sub,df_pupil$Run,df_pupil$Nback),]
# df_RT = df_RT[order(df_RT$sub,df_RT$Run,df_RT$Nback),]
# 
# df_pupil$RT = df_RT$RT
# df_pupil$Sleepiness = df2$Sleepiness
# df_pupil$Fatigue  = df2$Fatigue
# 
# df_pupil$lightNum = 0
# df_pupil[df_pupil$light=="high ipRGC",]$lightNum = 1
# 
# 
# df_pupil = aggregate( . ~ sub*light*Nback, data = df_pupil, FUN = 'mean')
# 
# modelList = c(
#   # "hit ~ lightNum + Sleepiness + Fatigue + (1+Run| sub)",
#   # "hit ~ Sleepiness + Fatigue + (1+Run| sub)",
#   # "hit ~ lightNum + Sleepiness + (1+Run| sub)",
#   # "hit ~ lightNum + Fatigue + (1+Run| sub)",
#   # "hit ~ Sleepiness + (1+Run| sub)",
#   # "hit ~ Fatigue + (1+Run| sub)",
#   # "hit ~ lightNum * Sleepiness * Fatigue + (1+Run| sub)",
#   # "hit ~ Sleepiness * Fatigue + (1+Run| sub)",
#   "hit ~ lightNum * Sleepiness * Fatigue + (1| sub)"
# )
# 
# df_pupil$hit <- scale(df_pupil$hit)[,1]
# df_pupil$RT <- scale(df_pupil$RT)[,1]
# df_pupil$lightNum <- scale(df_pupil$lightNum)[,1]
# df_pupil$Sleepiness <- scale(df_pupil$Sleepiness)[,1]
# df_pupil$Fatigue <- scale(df_pupil$Fatigue)[,1]
# 
# # estimateAll = NULL
# # aic_res = NULL
# # bic_res = NULL
# for( m in modelList){
#   inback= "2-back"
#   # for(inback in unique(df_pupil$Nback)){
#     
#     tmp_df = df_pupil[(df_pupil$Nback==inback),]
#     
#     # tmp_df = aggregate( . ~ sub*light*Nback, data = tmp_df, FUN = 'mean')
#     
#     eval(parse(text=paste0(" model_cand <- lmer(",m,", data=tmp_df)")))
#     # print(summary(model_cand))
#     sm = summary(model_cand)
#     # print(AIC(model_cand))
#     # fixef(model_cand)
#     # aic_res = c(aic_res,AIC(model_cand))
#     # bic_res = c(bic_res,BIC(model_cand))
#     
#     sm = summary(model_cand)
#     print(inback)
#     print(m)
#     print(sm$coefficients)
# }
# }

# eval(parse(text=paste0(" m <- lmer(",modelList[which.min(aic_res)],", data=tmp_df)")))
# eval(parse(text=paste0(" m <- lmer(",modelList[which.min(bic_res)],", data=tmp_df)")))
# 
# print(modelList[which.min(aic_res)])
# sm = summary(m)
# print(sm)


# tmp = data.frame(
#   Estimate = c(
#     # sm$coefficients["BP",]["Estimate"],
#     # sm$coefficients["PD_phasic",]["Estimate"],
#     sm$coefficients["Sleepiness",]["Estimate"],
#     sm$coefficients["Fatigue",]["Estimate"],
#     sm$coefficients["lightNum",]["Estimate"]),
#   factor = c(
#     # "Baseline",
#     # "Transient",
#     "Sleepiness",
#     "Fatigue",
#     "ipRGC"),
#   pVal = c(
#     # sm$coefficients["BP",]["Pr(>|t|)"],
#     # sm$coefficients["PD_phasic",]["Pr(>|t|)"],
#     sm$coefficients["Sleepiness",]["Pr(>|t|)"],
#     sm$coefficients["Fatigue",]["Pr(>|t|)"],
#     sm$coefficients["lightNum",]["Pr(>|t|)"]),
#   min = c(
#     # sm$coefficients["BP",]["Pr(>|t|)"],
#     # sm$coefficients["PD_phasic",]["Pr(>|t|)"],
#     sm$coefficients["Sleepiness",]["Estimate"]-sm$coefficients["Sleepiness",]["Std. Error"],
#     sm$coefficients["Fatigue",]["Estimate"]-sm$coefficients["Fatigue",]["Std. Error"],
#     sm$coefficients["lightNum",]["Estimate"]-sm$coefficients["lightNum",]["Std. Error"]),
#   max = c(
#     # sm$coefficients["BP",]["Pr(>|t|)"],
#     # sm$coefficients["PD_phasic",]["Pr(>|t|)"],
#     sm$coefficients["Sleepiness",]["Estimate"]+sm$coefficients["Sleepiness",]["Std. Error"],
#     sm$coefficients["Fatigue",]["Estimate"]+sm$coefficients["Fatigue",]["Std. Error"],
#     sm$coefficients["lightNum",]["Estimate"]+sm$coefficients["lightNum",]["Std. Error"]),
#   t = c(
#     # sm$coefficients["BP",]["Pr(>|t|)"],
#     # sm$coefficients["PD_phasic",]["Pr(>|t|)"],
#     sm$coefficients["Sleepiness",]["t value"],
#     sm$coefficients["Fatigue",]["t value"],
#     sm$coefficients["lightNum",]["t value"])
# )
# 
# tmp$formula = c(sm$call$formula)
# tmp$Nback = inback
# 
# estimateAll = rbind(estimateAll,tmp)

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

# f = list.files(folderName, pattern = "data_timeCourse_RunAve.json", full.names=T)
# df_question = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_question)){
#   df_question[[iName]] = unlist(df_question[[iName]])
# }
# 
# df_question = as.data.frame(df_question)
# 
# f = list.files(folderName, pattern = "df_targetAll", full.names=T)
# df_pupil = fromJSON(file=f[1])
# 
# for(iName in 1:length(df_pupil)){
#   df_pupil[[iName]] = unlist(df_pupil[[iName]])
# }
# 
# df_pupil = as.data.frame(df_pupil)
# df_pupil = aggregate( . ~ sub*Run*light*Nback, data = df_pupil, FUN = 'mean')
# 
# 
# # p = dispLineGraph(df_pupil,config,"hit",c("Run","Nback"))+
# #   facet_grid(. ~ Nback )
# 
# df_pupil = df_pupil[order(df_pupil$sub,df_pupil$Run,df_pupil$Nback),]
# df_question = df_question[order(df_question$sub,df_question$Run,df_question$Nback),]
# 
# df_pupil$Sleepiness = df_question$Sleepiness
# df_pupil$Fatigue  = df_question$Fatigue
# 
# df_pupil$lightNum = 0
# df_pupil[df_pupil$light=="high ipRGC",]$lightNum = 1
# 
# ##############################################################################
# # install.packages("semptools")
# library(lavaan)
# library(semPlot)
# library(semptools)
# 
# df_pupil["Light"] = 1
# df_pupil[df_pupil["light"]=="low ipRGC",]["Light"] = 0
# tmp_data = df_pupil
# # [df_pupil["Nback"]=="2-back",]
# 
# model <- '
#   hit ~ Light
#   hit ~ Sleepiness
#   hit ~ Fatigue
#   Sleepiness ~ Light
#   Fatigue ~ Light
#   Sleepiness ~~ Fatigue
# '
# 
# fit <- sem(model, data = tmp_data)
# 
# summary(fit, fit.measures = TRUE, standardized = TRUE)
# 
# m <- matrix(NA, 3, 3)
# m[1, 2] <- "hit"
# m[2, 2] <- "Light"
# m[3, 1] <- "Sleepiness"
# m[3, 3] <- "Fatigue"
# 
# p = semPaths(fit, 
#          # rotation = 2,
#          what = "std",
#          edge.label.cex = 1.2,
#          # layout = "tree2",
#          edge.width = 0.3,
#          fade = FALSE,
#          style = "ram", 
#          residuals = F,
#          nCharNodes = 0,
#          curvePivot = TRUE,
#          optimizeLatRes = TRUE,
#          intercepts = FALSE,
#          layout = m
# )
# 
# p_all$p_pa2 <- mark_sig(p, fit)
# p_all$p_pa2$size = c(4,3)
# 
# plot(p_all$p_pa2)

```

# Figure

```{r, message=FALSE, echo=FALSE, warning=FALSE, fig.width = 10, fig.height = 5}
if(saveFig){
  mmName = names(p_all)
  for(iFig in 1:length(mmName)){
    if("size" %in% names(p_all[[iFig]])){
      CairoPDF(file=paste0(saveFolder,iFig,"_",mmName[iFig]),
               width=p_all[[iFig]]["size"][[1]][1],
               height=p_all[[iFig]]["size"][[1]][2],
               bg = 'transparent')
      plot(p_all[[iFig]])
      dev.off()
    }else{}
  }
}
```
